The Impact of Tax Policy Evolution on Economic Development and Income Inequality

### 2024-02-20 paper/paper.qmd
Add simulation and test script

---
title: "The Impact of Tax Policy Evolution on Economic Development and Income Inequality"
author: 
  - Amie Liu, Wanling Ma
thanks: "Code and data are available at: https://github.com/WanlingMa/The-Impact-of-Tax-Policy-Evolution-on-Economic-Development-and-Income-Inequality; This reproduction was performed after a replication on the Social Science Reproduction platform: https://www.socialsciencereproduction.org/reproductions/0527a4db-9300-4160-ae8c-656c449f6d24/index"
date: today
date-format: long
abstract: "The role of taxation in economic development is crucial, influencing wealth distribution and shaping economic activity regulation. This paper uses R programming language to replicate and analyze data to understand the evolution of tax policy and its impact on income inequality and economic development. Our findings reveal a significant shift towards direct taxation as economies advance. Further research is necessary to address policy implementation challenges and refine optimal tax policy frameworks supporting equitable economic development."
format: pdf
number-sections: true
bibliography: references.bib
---

@@

target_year <- 2016

@@

ggplot(data, aes(x = gdppc, y = size_pit)) +
  geom_point(aes(color = color_group, shape = color_group)) +
  geom_smooth(method = "loess", color = "grey", formula = y ~ x, se = TRUE) + 
  scale_x_log10(labels = scales::comma, breaks = c(500, 1000, 2000, 5000, 10000, 25000, 50000)) +
  scale_color_manual(values = c("High GDP" = "forestgreen", "Medium GDP" = "purple", "Low GDP" = "sienna")) +
  scale_shape_manual(values = c("High GDP" = 15, "Medium GDP" = 18, "Low GDP" = 17)) +
  labs(x = "GDP per capita (Constant 2010 USD, log scale)", y = "Share of Workforce",
       subtitle = "Share of Workforce Legally Subject to Personal Income Tax") +
  theme_minimal() +
  theme(legend.position = "none",
        plot.background = element_blank(),
        panel.background = element_blank())
```

>>>>

---
title: "The Impact of Tax Policy Evolution on Economic Development and Income Inequality"
author: 
  - Amie Liu, Wanling Ma
thanks: "Code and data are available at: https://github.com/WanlingMa/The-Impact-of-Tax-Policy-Evolution-on-Economic-Development-and-Income-Inequality; This reproduction was performed after a replication on the Social Science Reproduction platform: https://www.socialsciencereproduction.org/reproductions/0527a4db-9300-4160-ae8c-656c449f6d24/index"
date: today
date-format: long
abstract: "The role of taxation in economic development is crucial, influencing wealth distribution and shaping economic activity regulation. This paper uses R programming language to replicate and analyze data to understand the evolution of tax policy and its impact on income inequality and economic development. Our findings reveal a significant shift towards direct taxation as economies advance. Further research is necessary to address policy implementation challenges and refine optimal tax policy frameworks supporting equitable economic development."
format: pdf
toc: true
number-sections: true
bibliography: references.bib
---

@@

target_year <- 2018

@@

ggplot(data, aes(x = gdppc, y = size_pit)) +
  geom_point(aes(color = color_group, shape = color_group)) +
  geom_smooth(method = "loess", color = "grey", formula = y ~ x, se = TRUE) + 
  scale_x_log10(labels = scales::comma, breaks = c(500, 1000, 2000, 5000, 10000, 25000, 50000)) +
  scale_color_manual(values = c("High GDP" = "forestgreen", "Medium GDP" = "purple", "Low GDP" = "sienna")) +
  scale_shape_manual(values = c("High GDP" = 15, "Medium GDP" = 18, "Low GDP" = 17)) +
  labs(x = "GDP per capita (Constant 2010 USD, log scale)", y = "Share of Workforce",
       subtitle = "Share of Workforce Legally Subject to Personal Income Tax") +
  theme_minimal() +
  theme(legend.position = "none",
        plot.background = element_blank(),
        panel.background = element_blank())
